\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{multicol}
\usepackage{fontawsome}
\input{glyphtounicode}

\usepackage[default]{sourcesanspro}
\usepackage[T1]{fontenc}

\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

\addtolength{\oddsidemargin}{-0.75in}
\addtolength{\evensidemargin}{-0.75in}
\addtolength{\textwidth}{1.5in}
\addtolength{\topmargin}{-0.75in}
\addtolength{\textheight}{1.5in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

\titleformat{\section}{
  \centering
}{}{0em}{}[\vspace{2pt} \color{black}\titlerule\vspace{2pt}]


\pdfgentounicode=1

\newcommand{\resumeItem}[1]{
  \item\normalsize{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{0.97\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & #2 \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.15in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

\begin{document}

\begin{center}
    {\fontsize{34pt}{34pt}\selectfont Manan Jain} \\

\end{center}


% %-----------Contact Info-----------
% \section{\Large Contact Info}
\begin{center}
        \setlength{\tabcolsep}{18pt}
    \begin{tabular}{c | c | c | c }
         {\underline{\faEnvelopeO \hspace{1pt} mananj0317@gmail.com}} & {\href{https://github.com/manan3172003}{\underline{\faGithub \hspace{1pt} GitHub}}} & {\href{https://www.linkedin.com/in/manan-jain-253486224/}{\underline{\faLinkedinSquare \hspace{1pt} LinkedIn}}} & {\faPhone \hspace{1pt} {+1 (587) 938 5436}}
    \end{tabular}{}
\end{center}

%-----------EDUCATION-----------
\vspace{-15pt}
\section{\LARGE Education}
  \resumeSubHeadingListStart
      \resumeSubheading
      {\large University of Alberta}{\large Expected: May 2026}
      {\normalsize{BSc Honors in Computer Science -- \textbf{GPA: 3.6}}}{\normalsize{Edmonton, AB}}
    \resumeSubheading
    {\normalsize{Awards: Faculty of Science Scholarship (2021-2023), Dean's Honor Roll (2022-2023) }}{}
    {}{}
  \resumeSubHeadingListEnd
  \vspace{-15pt}

%-----------EXPREIENCE-----------
\vspace{-10pt}
\section{\LARGE Experience}
  \resumeSubHeadingListStart

      \resumeSubheading
      {\large Invidi Technologies}{\large Edmonton, AB}
      {\normalsize{Software Engineer Intern}}{\normalsize{May 2024 -- Present}}
      \vspace{1pt}
      \resumeItemListStart
      \resumeItem{Contributed to the development of an ad targeting system using \textbf{Kotlin, Docker, and AWS}, optimizing the delivery of personalized advertisements across various platforms, enhancing \textbf{view count metrics by 20\%}.}
      \resumeItem{Designed and implemented an industries API to enforce competitive separation among advertisers, ensuring that competing companies' ads were not shown consecutively, enhancing compliance with industry regulations.}
      \resumeItem{Collaborated with a team of 8 developers to migrate the existing ad targeting system to a microservices architecture, reducing the \textbf{latency by 30\%}.}
      \resumeItem{Participated in the \textbf{on-call rotation} to provide 24/7 support for the ad campaign management system, ensuring that the system was always operational.}
      \resumeItem{Acted as \textbf{Scrum Master} for a team of 10 developers, leading daily standups, sprint planning, retrospective meetings, and ensuring smooth execution of iteration reviews across project timelines.}
      \resumeItemListEnd
      \vspace{5pt}

      \resumeSubheading
      {\large University of Alberta}{\large Edmonton, AB}
      {\normalsize{Undergraduate Teaching Assistant}}{\normalsize{January 2025 -- Present}}
      \vspace{1pt}
      \resumeItemListStart
      \resumeItem{Assisting in teaching \textbf{undergraduate and graduate students} the fundamentals of \textbf{parallel and distributed systems}, including \textbf{shared-memory and distributed-memory architectures}.}
      \resumeItem{Guiding students through \textbf{thread programming} and \textbf{data-parallel programming}, with a focus on optimizing performance in \textbf{high-performance computing} environments.}
      \resumeItem{Setup and maintained \textbf{HPC clusters} for students to run their parallel programs, ensuring that the clusters were \textbf{optimized for performance} and \textbf{scalability}.}
      \resumeItemListEnd
      \vspace{5pt}

      \resumeSubheading
      {\large UofA Blueprint}{\large Edmonton, AB}
      {\normalsize{Full-Stack Developer}}{\normalsize{Feb. 2023 -- Aug. 2023}}
      \vspace{1pt}
      \resumeItemListStart
        \resumeItem{Developed a web application for a \textbf{non-profit organization}, collaborating with a team of 12 developers.}
        \resumeItem{Engineered \textbf{frontend features} using \textbf{React} and optimized backend performance with \textbf{MongoDB}, achieving a \textbf{20\% reduction in loading time}.}
        \resumeItem{Refactored existing codebase, improving \textbf{code readability} and \textbf{maintainability}, resulting in a \textbf{25\% increase} in development efficiency for future features.}
      \resumeItemListEnd      
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\vspace{-10pt}
\section{\LARGE Projects}
 \vspace{3pt}
  \resumeSubHeadingListStart

  \resumeSubheading
  {\href{https://github.com/NatRunners/StudyAmp}{\underline{ StudyAmp (FastAPI, React, EEG Analysis) | NatHacks 2024 Winner} }}{}
  {}{}
  \vspace{-5pt}
  \resumeItemListStart
    \resumeItem{Built a \textbf{real-time attention monitoring system} using Muse 2 EEG and Brainflow, achieving \textbf{95\% accuracy} in tracking focus and live data synchronization.}
    \resumeItem{Engineered an \textbf{AI-powered focus analysis tool} with \textbf{Gemini API RAG LLM and Neural Networks}, improving focus retention by \textbf{30\%} and generating personalized summaries for low-focus segments.}
    \resumeItem{Developed a scalable \textbf{FastAPI backend} for real-time EEG data processing and audio analysis, supporting multi-user sessions efficiently.}
  \resumeItemListEnd

    \resumeSubheading
      {\href{https://github.com/CMPUT301W23T32/lordofthewings}{\underline{ GeoQR (Java, Android Studio)} }}{}
      {}{}
      \vspace{-5pt}
      \resumeItemListStart
        \resumeItem{Engineered an \textbf{Android application} that incentivizes social interaction and physical exercise through gamification,
        leveraging QR code collection as a core gameplay mechanic.}
        \resumeItem{Gained expertise in utilizing the \textbf{Google Maps API} and implemented the maps functionality, enabling users to view the locations of the scanned QR codes.}
        \resumeItem{Optimized load times and reduced crashes by \textbf{60\%} by implementing \textbf{threading and asynchronous programming in Java.}}
    \resumeItemListEnd

  \resumeSubHeadingListEnd


%-----------PROGRAMMING SKILLS-----------
\section{\LARGE Technical Skills}
\begin{itemize}[leftmargin=0.15in, label={}]
   \small{\item{
       {\resumeItemListStart
       \resumeItem{\textbf{Programming Languages}: Kotlin, Java, C++, Python, JavaScript, RISC-V Assembly, SQL}
       \vspace{1pt}
       \resumeItem{\textbf{Frameworks}: React, Express, Vue}
       \vspace{1pt}
       \resumeItem{\textbf{Developer Tools}: Android Studio, Git, Docker, Kubernetes, Amazon Web Services, MySQL, MongoDB}
   \resumeItemListEnd}
   }}
\end{itemize}

\end{document}
